%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Deekshita Aithal} \\ \vspace{1pt}
    \small +91-9164558449 $|$ \href{mailto:deekshitaaithal@gmail.com}
    {\underline{deekshitaaithal@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/deekshita-aithal-733428190}{\underline{https://www.linkedin.com/in/deekshita-aithal-733428190/}} $|$
\end{center}

\section{Summary}
\textbf{SAP Consultant with nearly 5 years of experience in industry. Skilled team leader adapt at
collaborating across departments to deliver innovative, client-focused solutions. Seeking to
leverage expertise in SAP ABAP to contribute effectively to a forward-thinking organization}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
     \resumeSubheading
      {Senior Software Engineer}{Mar 2021 -- Present}
      {Sony India Software Center}{Bengaluru, IN}
      \resumeItemListStart
        \resumeItem{\textbf{Joined as a Trainee Software Engineer after undergraduate. Moved up the ranks to become a Senior Software Engineer.}}
        \resumeItem{Took ownership of the \textbf{Analysis Office and Fiori platforms} in the projects.}
        \resumeItem{Leading \& Mentoring a 6 member team in business applications using SAP HANA}
        \resumeItem{Automated approval system to assist Business Users. Reduced \textbf{approx. 25 man hours of efforts.}}
         \resumeItem{Migrated reports to \textbf{AO platform that reduced memory consumption in the system}}
        \resumeItem{Provided \textbf{training and support to end users on SAP ABAP \& AO functionalities} ensuring smooth system integrations and user adoption.}
        \resumeItem{Conducted system analysis and troubleshooting to identify and resolve complex technical issues and performance bottlenecks.}
        \resumeItem{Continuously worked on \textbf{fixing performance issues in the system} across projects. Developed automations for reducing manual efforts}
        \resumeItem{Migration of ~2,000 SAP jobs from one platform to another. Handled the migration in phases and resolving the issues as needed.}
       \resumeItemListEnd
    \resumeSubHeadingListEnd

    \resumeSubHeadingListStart
        \resumeSubheading
        {Software Engineer}{Jul 2019 -- Mar 2021}
        {Sony India Software Center}{Bengaluru, IN}
         \resumeItemListStart
    
        \resumeItem{Developed numerous AO reports across projects. Handled adhoc requests for the same.}
        \resumeItem{Resolved \textbf{~300 incidents in a timely manner in the last 4 years}. Made sure to solve all the incidents on time with acute communication to the users.}
        \resumeItem{Support application for projects across different time zones.}
        \resumeItem{Contributed to documenting the project and all features that I was a part of.}
        \resumeItem{Setup \textbf{monitoring and alerting to users} for invalid authorization and built an better approval system for Vendor Invoice Management}
        \resumeItem{Developed features removing  duplicate logs inside logs. This helps developers for easier reading of logs.}
        \resumeItem{Developed a project where manual data entry of developers where automated. Created a system to migrate the changes from one system to another.}
        \resumeItem{Created a functionality for email trigger if there was a failure in Document Processed creation in VIM.}
        \resumeItem{Improved process flow of data to reduce issues in the customer's database. Developed a flow for moving data across different projects.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd
     
  


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor's of Engineering in Computer Science}{Aug. 2015 -- Aug 2019}
      {NMAM Institute of Technology, CGPA: 8.80}{Udupi, India}
    \resumeSubheading
      {Pre University College}{Aug. 2013 -- May 2015}
      {Vidyodaya P.U College, Percentage: 91}{Udupi, India}
  \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Spoken Languages}{: German(A1, Undergoing), English} \\
     \textbf{Programming Languages}{: ABAP on HANA, SQL} \\
     \textbf{Technologies}{: Fiori, Analysis Office, BEX, VIM, CDS, SLT} \\
     \textbf{Databases}{: SAP} \\
     \textbf{Skills}{: ABAP Programming}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
