%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Rajath Aithal} \\ \vspace{1pt}
    \small +91-9591294419 $|$ \href{mailto:rajathaithal@gmail.com}
    {\underline{rajathaithal@gmail.com}} $|$ 
    \href{https://linkedin.com/in/rajathaithal}{\underline{linkedin.com/in/rajathaithal}} $|$
    \href{https://github.com/ayerajath}{\underline{github.com/ayerajath}} $|$
    \href{https://ayerajath.github.io}{\underline{rajathaithal.com}} \\
\end{center}

\section{Summary}
\textbf{Experienced Software Engineer with around 5 years of professional experience. A curious individual with a love for data, databases, and building scalable systems}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
     \resumeSubheading
      {Software Engineer}{Mar 2024 -- Present}
      {LaunchDarkly (acquired from Houseware)}{Bengaluru, IN}
      \resumeItemListStart
        \resumeItem{Joined LaunchDarkly as part of the Houseware acquisition; continued owning Product Analytics and the Warehouse Scale team.}
        \resumeItem{Took \textbf{ownership of the Product Analytics infrastructure stack}. Used Terraform as IaC; worked on the observability layer with OpenTelemetry and Datadog.}
        \resumeItem{Integrated and delivered Product Analytics capabilities across the LaunchDarkly product suite; partnered with product teams to ship features end-to-end.}
        \resumeItem{Worked on improving runtimes of the data export DAG; \textbf{improved query runtimes by almost 50\%}.}
        \resumeItem{Delivered a hosted Product Analytics solution in LaunchDarkly built on top of ClickHouse; built/maintained data pipelines for ClickHouse.}
        \resumeItem{\textbf{Built hosted Product Analytics on ClickHouse}; developed/maintained pipelines; supported warehouse workloads (\textbf{Snowflake/BigQuery/Databricks}) and worked with CDP tools like Segment.}
        \resumeItem{Built AI agents for Product Analytics and Web Analytics; the agent ranked in the Top 10 on Product Hunt.}
      \resumeItemListEnd

    \resumeSubheading
      {Senior Software Engineer - SDE II}{Jan 2022 -- Feb 2024}
      {Playsimple Games}{Bengaluru, IN}
      \resumeItemListStart
        \resumeItem{\textbf{Part of the data/backend engineering team.}}
        \resumeItem{\textbf{Led the Integrations pod} to deliver features \& bug fixes within costs and time. Handled all integrations related work. Integrated numerous external data sources and ingesting GBs of data within SLAs. Developed data pipelines using \textbf{Airflow, Spark, Redshift, Python, Databricks.}}
        \resumeItem{Developed a REST API using \textbf{Golang to store event data from games}. Ingests \textbf{8 billion events per day}. \textbf{Able to handle 4,000 requests/s.}}
        \resumeItem{Developed another REST API using \textbf{Golang to handle 32,000 requests/s}. Ingests close to \textbf{3 billion events every day.}}
        \resumeItem{Ingest close to \textbf{600 GB of data everyday}. Manage and monitor the infrastructure for atmost uptime.}
        \resumeItem{Reduced infrastructure costs \textbf{saving upwards of 5000\$ every year(60\%)} by applying various techniques like right sizing EC2 instances or load balancer.}
        \resumeItem{Handled various security related infrastructure issues. Updated AWS configurations and followed best practices for infra security.}
        \resumeItem{As a tech lead for team, brainstormed many ideas and successfully took them to production along with team.}
        \resumeItem{Stabilized current work \& team to be able to handle more charters}
      \resumeItemListEnd

    \resumeSubheading
      {Analyst - Software Engineer}{Jan 2020 -- Jan 2022}
      {Cardinal Health}{Bengaluru, IN}
      \resumeItemListStart
        \resumeItem{Joined post-undergraduate and worked on the Order Express Android team}
        \resumeItem{Developed and maintained analytics layer for Order Express.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {NMAM Institute of Technology}{Udupi, India}
      {B.Tech in Computer Science. GPA: 9.00}{Aug. 2016 -- Aug 2020}
  \resumeSubHeadingListEnd



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, GoLang, Java, SQL} \\
     \textbf{Technologies}{: Clickhouse, Databricks, Snowflake, Spark, Linux, Design Patterns, Kafka, Docker, Kubernetes, Firebase, Datadog} \\
     \textbf{Cloud}{: AWS, GCP, DigitalOcean} \\
     \textbf{Databases}{: Redshift, Delta, Bigquery, Postgres, MongoDB, Snowflake, Clickhouse} \\
     \textbf{Skills}{: Data Engineering, Databases, Backend Development, Infrastructure Security, AI development}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
